---
title: "swim data vignette"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{swim_data_vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(SwimDataAnalysis)
```

This package is to analyze a swimmer's data from [swimcloud.com](swimcloud.com). The functions are tested on data that has been copy-pasted from the Times page of a swimmer's swimcloud page for a single event.

# Examples:

## cleanData
Description: used to make a variable with time series and coerce date var to date type
```{r}
#| eval: false
cleanData(twohundred_fly)
```

## filter_year
Description: used to filter for all listed times in the specified year (not season)
```{r}
#| eval: false
filter_year(twohundred_fly, 2025)
```

## find_meet
Description: used to find the times from a meet, regardless of year
```{r}
#| eval: false
find_meet("Speedo Sectionals - Providence")
```

## plot_progress
Description: used to plot progressions in time throughout the years
```{r}
#| eval: false
plot_progress(twohundred_fly)
```

## find_event
Description: used to filter to a specific event (if data includes more than one)
```{r}
#| eval: false
find_event(top_three, "200 Back")
```

## yearly_pr
Description: used to find the pr for a certain year
```{r}
#| eval: false
yearly_pr(twohundred_fly, 2026)
```

## make_time_sec
Description: used to add a time_sec variable that converts times to seconds
```{r}
#| eval: false
make_time_sec(clean_twohundred_fly)
```

## moving_avg
Description: used to create a plot with times and moving average
```{r}
#| eval: false
moving_avg(twohundred_back)
```

## plot_meet_type
Description: used to create a plot times sectioned by meet type
```{r}
#| eval: false
plot_meet_type(twohundred_back)
```
